---
title: "PractStatDay1"
author: "Rakyan Satrya Adhikara"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Descriptive Staristics
Have a well-described data without generalization

```{r}
gas <- c(8,6,7,8,8,5,9,8,6,8,9,1,5,105,9,6,8,10,7,8)
length(gas)
oil <- c(4,2,4,6,7,3,7,8,9,9,6,4,2,18,16,13,2,12,10,7)
retail <- read.csv("data_input/workshop.csv")
```

## The Center of Data
### Mean
Most well-used function: Mean.

Desciptive Statistics: Mean is commonly used for the center of data.
Statistical Inference: Mean is commonly used for moving average data-time series.

Pro and Con:
(+)
(-) Not very accurate for making is as an expectation (Not very representative)

```{r}
mean(gas)
mean(oil)
```

### 'Trimmed Mean'
add a 'trim' parameter at the 'mean' function. the number as the parameter input has to be in percentage.

NOTE: You can't cut more than 5% of total data.

```{r}
mean(gas,trim = 0.05)
```

### Median
Most common alternative function: Median

Data division concept:
divided by 2: Min |-------------| Median |-------------| Max
divided by 4: Min |--| 1st Q |--| Median |--| 3rd Q |--| Max

Pros and Cons;
(+) Rarely get some outlier (Robust)
(-) Too robust

Common functions to get median:
- median()
- fivenum()
- quantile()
  NOTE: You can display a specified part of quantile() by adding the name as the next parameter
- summary()

```{r}
median(gas)

fivenum(gas)

quantile(gas)

summary(gas)
```

```{r}
profit_var <- retail[,c("Profit")]
summary(profit_var)
```

### Mode
Unfortunately, there is no official function to get mode.
However, there is a custom function to get mode.

### 'Common' Range

```{r}
max(gas)-min(gas)
diff(range(gas))
```

### Interquartile Range (IQR)
Difference of 1st quartile and 3rd quatrile

```{r}  
IQR(gas)
```

Upper Whisker / outer Fence: Q3 + k (1.5) * IQR
Lower Whisker / Inner Fence: Q1 - k (1.5) * IQR

```{r}
# Upper Whisker / Outer Fence
UpperW <- quantile(gas,0.75) + (1.5*IQR(gas))
LowerW <- quantile(gas,0.25) - (1.5*IQR(gas))
gas[gas>UpperW]
```

### Variance and standard deviation

Variance:

Way #1: use var() function

Way #2: 

Standard Deviation: Squareroot of Variance

```{r}
var_gas <- var(gas)
var_oil <- var(oil)
sum((gas-mean(gas))^2)/(length(gas)-1)

sd(gas)
sqrt(var_gas)
mean(profit_var)
sd(profit_var)/sqrt(length(gas)-1)
```

## Distribution
### Covariance and Correlation

Covariance usually used only to compare if both values have the same behaviour
Correlation is similar to probablility. If the value is getting into 1, the behaviour of both values become more equal and so the opposite.

```{r}
cov(oil,gas)
cor(oil,gas)
```

```{r}
hist(gas, breaks = 1000)
plot(density(gas))
plot(density(oil))
```

### Normal Distribution
Characteristics:
1. Bell curve
2. Symetrical
3. Mean = Median = Mode
4. Uni-Mode